---
name: Marcus Munch
surname: Grünewald
position: "Data Scientist"
profilepic: "marcus.png"
www: marcusmunch.dk
email: "`r URLdecode('%68%65%6C%6C%6F%40%6D%61%72%63%75%73%6D%75%6E%63%68%2E%64%6B')`"
github: marcusmunch
linkedin: marcusmunch
aboutme: Data scientist with a background in microbiology
date: "`r format(Sys.Date(), '%b %y')`"
headcolor: 333333
output:
  vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

The story goes that I got my first computer at about 10 years old --- and never looked back since then.
I've always loved finding patterns in complex systems, and picking up programming was therefore a no-brainer for me.
"Hidden in plain sight" to me describes both microbiology and data science, and it therefore makes perfect sense to combine the two.

```{r}
# Prepare the data

all_files <- list.files("resources/cv/", pattern = "*.ya?ml", full.names = TRUE)

list <- lapply(all_files, \(.x) {
  dplyr::bind_rows(yaml::read_yaml(.x))
})

names(list) <- gsub("[.][^.]*$", "", basename(all_files))

invisible(list2env(list, envir = .GlobalEnv))

if (interactive()) print(list[1])
```

# Work experience
During my years at Statens Serum Institut, I have worked on expanding my data science skills to become greatly familiar with working in SQL databases as well as developing an R package for effectively keeping track of data over time.

Despite the academic team at TestCenter Danmark being my very first position after graduating, I was trusted with many responsibilities.
The swiftly changing setting put on us by covid-19 taught me to keep my head calm in pressured situations and gave me a lot of invaluable experience.

```{r work}
vitae::detailed_entries(work,
                        what = title,
                        when = year,
                        with = department,
                        where = workplace,
                        why = details)
```

## Programming experience
This CV was written in Rmarkdown, building individual sections from YAML files.
The resulting PDF was built using pandoc on Linux.
The source files are hosted on a GitHub repository which also builds my personal website, including this CV.

In summary, I am confident working with (among others):

* R, including
  - The tidyverse
  - Package development
  - Automated report generation with Rmarkdown
* Python
  - Scraping and text mining
  - Automating simple tasks such as file organising with minimal required input
* Git, including GitHub and GitHub Actions
* SQL
  - Postgres, MSSQL and the abomination that is SQLite
* Linux (Ubuntu), including bash

\newpage

# Education
The increasing sensitivity of techniques in biology and medicine combined with increased availability of computing power drive a large demand for knowledge of both areas.
Because of this, I tailored my MSc in biology for high-throughput analysis and data automation.

```{r education}
sorted_degrees <- education |>
  dplyr::filter(sort) |>
  dplyr::distinct(degree) |>
  dplyr::pull()

education <- education |>
  dplyr::group_by(degree) |>
  dplyr::mutate(courses = ifelse(degree %in% sorted_degrees, sort(courses), courses)) |>
  dplyr::ungroup()

education |>
  vitae::detailed_entries(what = degree,
                          when = year,
                          with = institution,
                          where = where,
                          why = courses,
                          .protect = FALSE)
```

# Outside work
When I need to untangle my mind after a day of data exploration, I thankfully have numerous ways of doing so.
While I do enjoy fiddling with various small programming projects on my Raspberry Pi at home, I also enjoy music a lot, having both played drums in a number of bands as well as in student revues during my time at university, where I have also sung and directed.

I live in Østerbro, Copenhagen with my girlfriend and our two year-old daughter, who is about as fond of music as myself, and when I want to go completely off the radar, I enjoy few things more than a walk, talk or dance with her.
